### 2015-07-05 paper.tex
convert the rate of Rn at 0.7MeV cut from 17.31Hz to 15.94Hz

		\subsection{Natural radioactivity estimation}
		Natural radioactivity exists in the materials of central 
		detector.
		The materials of central detector in the acrylic option mainly
		include LS, acrylic, oxygen-free copper, stainless steel, as
		well as the glass of PMT.
		The formations of these materials in different conditions 
		cause more or less existence of radioelement.
		The Rn in the water pool also induced radioactivity.
		The singles rate of each material's natural radioactivity 
		in different energy threshold is 
		listed in table.1. The detailed discussion can be found in
		the reference\cite{lab3}.

	\end{multicols}
	\begin{center}
		\tabcaption{ \label{tab1}  The inner singles rates}
		\footnotesize
		\begin{tabular*}{170mm}{@{\extracolsep{\fill}} c c c c c c c c}
			\toprule  Singles Rate(Hz)&LS &Glass &Acrylic  &Steel &Copper &Rn &Sum \\
			\hline
			E$>$0.7MeV &2.39   &2.43  &69.23  &0.89  &0.82 &17.31   &93.07  \\
			E$>$0.6MeV &4.26   &2.66  &75.26  &0.95  &0.94 &19.79   &103.86 \\
			E$>$0.5MeV &12.06  &2.83  &81.49  &0.98  &1.06 &23.36   &121.78 \\
			E$>$0.4MeV &13.86  &3.24  &87.84  &1.22  &1.29 &26.11   &133.56 \\
			E$>$0.3MeV &15.51  &3.72  &98.57  &1.57  &1.51 &31.60   &152.48 \\
			E$>$0.2MeV &17.16  &4.12  &117.33 &1.80  &1.89 &39.85   &182.15 \\
			E$>$0.1MeV &352.36 &5.27  &149.26 &2.22  &2.60 &54.97   &566.68 \\
			\bottomrule
		\end{tabular*}
	\end{center}
	\begin{multicols}{2}

>>>>

		\subsection{Natural radioactivity estimation}
		Natural radioactivity exists in the materials of central 
		detector and the rock around the water pool.
		The materials of central detector in the acrylic option mainly
		include LS, acrylic, oxygen-free copper, stainless steel, as
		well as the glass of PMT.
		The formations of these materials in different conditions 
		cause more or less existence of radioelement.
		The Rn in the water pool also induced radioactivity.
		The singles rate of each material's natural radioactivity 
		in different energy threshold is 
		listed in table.1. The detailed discussion can be found in
		the reference\cite{lab3}.

	\end{multicols}
	\begin{center}
		\tabcaption{ \label{tab1}  The inner singles rates}
		\footnotesize
		\begin{tabular*}{170mm}{@{\extracolsep{\fill}} c c c c c c c c}
			\toprule  Singles Rate(Hz)&LS &Glass &Acrylic  &Steel &Copper &Rn &Sum \\
			\hline
			E$>$0.7MeV &2.39   &2.43  &69.23  &0.89  &0.82 &15.94   &91.7  \\
			E$>$0.6MeV &4.26   &2.66  &75.26  &0.95  &0.94 &19.79   &103.86 \\
			E$>$0.5MeV &12.06  &2.83  &81.49  &0.98  &1.06 &23.36   &121.78 \\
			E$>$0.4MeV &13.86  &3.24  &87.84  &1.22  &1.29 &26.11   &133.56 \\
			E$>$0.3MeV &15.51  &3.72  &98.57  &1.57  &1.51 &31.60   &152.48 \\
			E$>$0.2MeV &17.16  &4.12  &117.33 &1.80  &1.89 &39.85   &182.15 \\
			E$>$0.1MeV &352.36 &5.27  &149.26 &2.22  &2.60 &54.97   &566.68 \\
			\bottomrule
		\end{tabular*}
	\end{center}
	\begin{multicols}{2}
